---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# assignmentB2

<!-- badges: start -->
<!-- badges: end -->

The goal of the package `assignmentB2` is to calculate the summary statistics (min, max, mean, median) and create a boxplot of a variable in a data frame across different groups more conveniently.

## Installation

This package is not yet on [CRAN](https://CRAN.R-project.org). But you can download it from this repository using the following [R](https://www.r-project.org/) command.

``` r
devtools::install_github("stat545ubc-2021/Yitong_Zhao_AssignmentB", ref = "0.1.0")
```

## Example

This is a basic example which shows you how to use the function `summary_and_boxplot_by_group()` in this package:

```{r}
suppressPackageStartupMessages(library(assignmentB2))
summary_and_boxplot_by_group(datateachr::apt_buildings, property_type, no_of_storeys)
```

You can also specify the argument `alpha` and `scale_y` change the default transparency and scale the y-axis of the boxplot to make it look better.

```{r}
summary_and_boxplot_by_group(datateachr::apt_buildings, property_type, no_of_units,
                             alpha = 0.4, scale_y = TRUE)
```

More instructions about how to use the function `summary_and_boxplot_by_group()` can be found using the following command:

```r
?summary_and_boxplot_by_group
```
